\chapter{References}

\begin{enumerate}[label={\Alph*.}]
  \item \textbf{Books}
        \begin{itemize}
          \item Cohn, M. (2020). \textit{Succeeding with Agile: Software Development Using Scrum} (2nd ed.). Addison-Wesley Professional. ISBN: 978-0321579362.
        \end{itemize}
  \item \textbf{Academic and Educational Resources}
        \begin{itemize}
          \item Theobald, S., Diebold, P., \& Schmitt, A. (2021). Comparing scaling agile frameworks based on underlying practices. \textit{International Journal of Agile Systems and Management}, 14(1), 1-25.
        \end{itemize}
  \item \textbf{Online Resources and Documentation}
        \begin{itemize}
          \item Agile Alliance. (2024). \textit{Agile 101}. Retrieved from \url{https://www.agilealliance.org/agile101/}
          \item Scrum.org. (2024). \textit{The Scrum Guide}. Retrieved from \url{https://scrumguides.org/}
          \item Atlassian. (2024). \textit{Agile Coach: Agile tutorials, videos and programs}. Retrieved from \url{https://www.atlassian.com/agile}
          \item Kanban University. (2024). \textit{What is Kanban?} Retrieved from \url{https://kanban.university/kanban-guide/}
          \item Scaled Agile Framework. (2024). \textit{SAFe 6.0 Framework}. Retrieved from \url{https://scaledagileframework.com/}
          \item Project Management Institute. (2023). \textit{Agile Practice Guide}. Retrieved from \url{https://www.pmi.org/pmbok-guide-standards/practice-guides/agile}
          \item Version One. (2023). \textit{15th Annual State of Agile Report}. Retrieved from \url{https://stateofagile.com/}
          \item Scrum Alliance. (2024). \textit{Scrum Resources and Community}. Retrieved from \url{https://www.scrumalliance.org/}
          \item LeanKit. (2024). \textit{Kanban Roadmap: How to Get Started}. Retrieved from \url{https://leankit.com/learn/kanban/kanban-roadmap/}
          \item AgileManifesto.org. (2024). \textit{Manifesto for Agile Software Development}. Retrieved from \url{https://agilemanifesto.org/}
          \item Microsoft DevOps. (2024). \textit{What is DevOps?} Retrieved from \url{https://azure.microsoft.com/en-us/overview/what-is-devops/}
          \item GitHub. (2024). \textit{GitHub Flow: A lightweight, branch-based workflow}. Retrieved from \url{https://guides.github.com/introduction/flow/}
          \item Docker. (2024). \textit{What is a Container?} Retrieved from \url{https://www.docker.com/resources/what-container}
          \item Jenkins. (2024). \textit{Jenkins User Documentation}. Retrieved from \url{https://www.jenkins.io/doc/}
        \end{itemize}
\end{enumerate}